Manuscript draft

### 2019-06-25 manuscript/manuscript draft.Rmd
updated manuscript draft to include table with sample sizes and number of plots

| Variable | Definition | Components included | Methodologies used|
|--------------|-------------------|-------------|------------------------|
| GPP | Annual gross primary production; annual uptake of carbon dioxide by an ecosystem | NA | Flux partitioning of eddy covariance |
| NPP_1 | Annual net primary production; the component of GPP that is stored in plant tissue; GPP minus ecosystem respiration | Foliage, branch, stem, coarse root and fine root | Direct measurement of annual increments of components | 
| NPP_2 | Annual net primary production; the component of GPP that is stored in plant tissue; GPP minus ecosystem respiration | Foliage, branch, stem, coarse root, fine root, and understory | Direct measurement of annual increments of components |
| ANPP_1 | Aboveground net primary production | Foliage and stem | Direct measurement of annual increments of components | 
| ANPP_2 | Aboveground net primary production | Foliage, stem, and branch | Direct measurement of annual increments of components |
| ANPP_foliage | Net primary production of foliage | Foliage | Direct measurement of litterfall, correcting for changes in leaf biomass when measured |
| ANPP_woody | Net primary production of woody components | Stems and branches | Direct measurement of stem growth and branch fall |
| ANPP_woody_stem | Net primary production of woody stems | Woody stems | Direct measurement of stem growth increment |
| BNPP_root | Belowground net primary production | Coarse and fine roots | Direct measurement of one or more of: fine root turnover, soil cores, root ingrowth cores, minirhizotrons; indirect estimates of coarse roots using allometries based on aboveground stem increment measures |
| BNPP_root_fine | Net primary production of fine roots | Fine roots | Direct measurement of one or more of: minirhizotrons, fine root turnover, soil cores, root ingrowth cores |

>>>>

| Variable | Definition | Components included | Methodologies used | Number of records | Number of plots |
|--------------|-------------------|-------------|------------------------|-------|-------|
| GPP | Annual gross primary production; annual uptake of carbon dioxide by an ecosystem | NA | Flux partitioning of eddy covariance | 254 | 91 |
| NPP_1 | Annual net primary production; the component of GPP that is stored in plant tissue; GPP minus ecosystem respiration | Foliage, branch, stem, coarse root and fine root | Direct measurement of annual increments of components | 93 | 79 |
| NPP_2 | Annual net primary production; the component of GPP that is stored in plant tissue; GPP minus ecosystem respiration | Foliage, branch, stem, coarse root, fine root, and understory | Direct measurement of annual increments of components | 23 | 23 |
| ANPP_1 | Aboveground net primary production | Foliage and stem | Direct measurement of annual increments of components | 140 | 131 |
| ANPP_2 | Aboveground net primary production | Foliage, stem, and branch | Direct measurement of annual increments of components | 119 | 77 |
| ANPP_foliage | Net primary production of foliage | Foliage | Direct measurement of litterfall, correcting for changes in leaf biomass when measured | 100 | 96 |
| ANPP_woody | Net primary production of woody components | Stems and branches | Direct measurement of stem growth and branch fall | 53 | 50 |
| ANPP_woody_stem | Net primary production of woody stems | Woody stems | Direct measurement of stem growth increment | 264 | 252 |
| BNPP_root | Belowground net primary production | Coarse and fine roots | Direct measurement of one or more of: fine root turnover, soil cores, root ingrowth cores, minirhizotrons; indirect estimates of coarse roots using allometries based on aboveground stem increment measures | 105 | 90 |
| BNPP_root_fine | Net primary production of fine roots | Fine roots | Direct measurement of one or more of: minirhizotrons, fine root turnover, soil cores, root ingrowth cores | 96 | 88 |
